Linear Regression (TMAs)

### 2020-01-09 rmds/linear_regression.Rmd
small updates

# should find better way to read data from rmd folder
lm_dat <- readRDS('/Users/mcknigri/Documents/honors/honors-project/data/modeling-dat/lm_dat_scaled.RDS')
```

@@

>>>>

# should find better way to read data from rmd folder
lm_dat <- readRDS('~/Documents/honors/honors-project/data/modeling-dat/lm_dat_scaled.RDS')
```

@@

lm_dat_small <- lm_dat %>% 
  dplyr::select(-c(GEOID, daily_boards_per_stop, sqkm, perc_transit_comm, log_daily_boards, log_daily_stops))
